---
title: "Untitled"
output: html_document
---





## Descriptives

```{r include=FALSE}
library(tidyverse)
tc_location <- '/home/jtimm/jt_work/GitHub/twitter_corpus/'
R.utils::sourceDirectory(paste0(tc_location, 'fns/'), 
                         modifiedOnly = TRUE)
```


```{r message=FALSE, warning=FALSE}
korpus <- load_lawmaker_tweets()

xsum1 <- korpus %>%
  mutate(tokens = tokenizers::count_words(text),
         yr = gsub('-.*', '', created_at))

xsum2 <- xsum1 %>%
  group_by(congress, yr) %>%
  summarise(tweets = n(),
            tokens = sum(tokens),
            handles = length(unique(toupper(screen_name))),
            ave = round(tokens/tweets, 1),
            dates = paste0(min(created_at), ' : ', 
                           max(created_at))) %>%
  mutate(tweets = formatC(tweets, big.mark = ','),
         tokens = formatC(tokens, big.mark = ','))

xsum2 %>% knitr::kable()
```


---

1. Average length of tweets (in words) increased substantially from 2017 to 2018; presumably a result of Twitter’s increased character limit from 140 to 280 at the end of 2017.

2. Total number of Twitter lawmaker accounts roughly doubled from the 115th congress to the 116th. 

The latter, presumably a function of the inclusion of both office & campaign Twitter accounts.  It is not clear if this is per some methodological change on the part of GWU, or a result of more lawmakers in 116 using more than one account.


---


```{r fig.height=6, message=FALSE, warning=FALSE}
xsum1 %>%
  group_by(congress, yr, created_at) %>%
  summarise(tweets = n(),
            tokens = sum(tokens),
            ers = length(unique(screen_name))) %>%
  ungroup() %>%
  mutate(moving_n = zoo::rollmean(tweets, 
                                  k = 60, 
                                  fill = NA)) %>%
  ggplot() +
  geom_line(aes(x = created_at, 
                y = tweets)) +
  
    geom_line(aes(x = created_at,
                y = moving_n),
            color = 'steelblue',
            #linetype = 2,
            size = 0.75) +
  theme_bw() +
  ggtitle('Total daily tweets: US Congresses 115 & 116')
```



